\section{Exercise 04: SQL Injection}

\subsection{SQL Injection}
\subsubsection{Does it mean the MySQL server is protected against cyber attacks? From Kali,try:mysql -h <METASPLOITABLE IP> -P 3306}
\subsubsection{How could that protection look like?}
\subsubsection{And what exactly would it protect against?}

\subsection{Spying with SQL Injection}
\subsubsection{Please shortly discuss your opinion of this web servers configurationconcerning directly listings.}
\subsubsection{What type of SQLi attack works? Can you explain why?}
\subsubsection{What is the \# sign for? Can we generally assume it to do the trick?}
\subsubsection{Include four relevant username/password combinations in your report.What is the issue with the passwords in the data base and what could bedone to secure them?}
\subsubsection{Which other problem allows you to get into the machine using ssh? Howcould this be prevented?}

\subsection{Elevation of Privilege}
\subsubsection{Which are the individual issues that allowed us to go from a web interfaceto root access, and how would you address them as a servers operator toprevent them being exploited? Describe the issues you identified and tryto come up with suggestions on how to fix them.}
\subsubsection{Can SQL Injection expose an otherwise inaccessible data base server?}
\subsubsection{How likely do you think an attack scenario as presented here is?}

\subsection{Using our Foot in the Door for Access to Other Services}
\subsubsection{Is sudo necessary? What do we gain by using it?}
\subsubsection{Are there other ways to search for a file? Which do you know?}
\subsubsection{What was the problem with the web application?}
\subsubsection{Which ports and services were the problem associated with?}
\subsubsection{How did you exploit the vulnerability?}
\subsubsection{And what were you able to do?}
\subsubsection{How would you suggest to fix the problem? (Do some online research aboutSQL injections solutions.)}
\subsubsection{Draft a shortly and crisply, the relevant parts of a policy trying to prevent theseissues.}
text

\subsection{Fully Explore Local Accounts}
\subsubsection{What are benefits of performing this scan after already having full access?}


\subsection{Post-Exploitation}
\subsubsection{Thinking as an attacker, what would your next steps be?}
\subsubsection{As an operator, what would you do to counteract?}

\subsection{Obfuscated Malware}
\subsubsection{Task 1 - Take your time to look at the code. Is it readable?}
\subsubsection{Task 3 - What does the code do? Is it a malicious software and if so how wouldyou classify it?}
